Illusory Finger Stretching and Somatosensory Responses

### 2025-03-19 manuscript.qmd
Check using correct python version

# create python environment and install packages
  # # if (processdata==1){
  # install_miniconda()
  # use_miniconda('r-reticulate')
  # # install_python(version="3.10")
  # py_install(c('mne', 'numpy', 'scikit-learn', 'matplotlib', 'pandas', 'openpyxl'))
  # # }
# use_python("/usr/bin/python3.10")

>>>>

# create python environment and install packages
OS <- Sys.info()['sysname']
if (OS=='Linux'){use_python("/usr/bin/python3.10")}
if (OS!='Linux'){
  install_miniconda()
  use_miniconda('r-reticulate')
  # install_python(version="3.10")
  py_install(c('mne', 'numpy', 'scikit-learn', 'matplotlib', 'pandas', 'openpyxl'))
}
